---
title: "linreg"
author: "Group 19"
date: "28/09/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package lab4
This is the package for the lab4 of the Advanced R programming course. This package performs the linear regression with two argument: formula and data. formula is the formula object indicating the dependent and independent variables.  

## Useage:

```{r }
# Install the library:
devtools::install_github("lmxblur/Adv_lab4", subdir="lab4")

# Import a dataset
data(iris)

# Create an object
lr_model <- linreg$new(formula = Petal.Length~Species, data = iris)
```

## Methods inside the pacakge

### print(): Print out the coefficient and  name of the coefficient of the linear regression.

```{r }
lr_model$print()
```

### plot(): Return two plots in a list. First the Residuals vs Fitted Values and second the Square of Standartized residuals vs Fitted values. .

```{r }
lr_model$print()
```

### resid(): Return the vector of residual.

```{r }
lr_model$resid()
```

### pred(): Return the predicted values yˆ.

```{r }
lr_model$pred()
```

### coef(): Return the coefficients as a named vector.

```{r }
lr_model$coef()
```

### summary(): Returns the coefficients with their standard error, t-value and p-value as well as the estimate of σˆ and the degrees of freedom of the model.

```{r }
lr_model$summary()
```

